\mytitle{}

### 2019-07-31 paper/paper.tex
Just the conclusion + new results to be handled...

\section{Introduction}

Network anomaly detection and intrusion detection/prevention are continually evolving problems, compounded by the partial, non-\emph{independent and identically distributed} (IID) view of data at each point in the network.
Attacks and anomalous behaviours evolve, becoming more sophisticated or employing new vectors to harm a network or system's confidentiality, integrity, and availability without being detected \cite{DBLP:journals/comsur/BhuyanBK14}.
These attacks and anomalies have measurable consequences and symptoms which allow a skilled analyst to infer new signatures for detection by misuse-based classifiers, but unseen attacks may only be defended against after-the-fact.
This issue is inherent to \emph{misuse-} or \emph{signature-based} intrusion detectors, and it has been long-hoped that \emph{anomaly-based} detectors would surpass this by making effective use of statistical measures \cite{DBLP:journals/comsur/BhuyanBK14}.

@@

%?? Discuss the most important conclusions before the outline.
We find that the existing work for this task fails to account for congestion-aware traffic (i.e., TCP) and deployment environments with high host density per egress point, achieving poor results due to an overly coarse view of the network.
The approach we identify to remedy this is to make throttling decisions on a per-source basis, and we present the engineering decisions this mandates: updating RL agents from multiple traces per timestep, timed random sequential action computation and a supporting \emph{software-defined network} (SDN) architecture.
In tandem with the development and evaluation of an effective state space and model, we provide the design of a second model inspired by past work on algorithmic DDoS prevention, as an example of the integration of domain-specific knowledge.
Our introduction of per-source decisions improves substantially upon the state-of-the-art when acting upon most internet traffic (i.e., congestion-aware protocols), and we show that our second model achieves excellent performance for high host density in this case.
Crucially, both models remain protocol- and content-agnostic to offer future-proofing against the rollout of future protocols like QUIC \cite{DBLP:conf/sigcomm/LangleyRWVKZYKS17}.
%?? Also algorithmic enhancements such as multiple actions per timestep, 
%?? PROTOCOL-AGNOSTIC -- HOW WILL THESE THINGS COPE WITH QUIC ET AL.?!?!
Briefly, this paper contributes:
\begin{itemize}
%	\item A DDoS mitigation system based on direct-control reinforcement learning, designed for deployment in real-world software-defined networks (\cref{sec:environment-and-rl-algorithm,sec:acting-on-individual-sources}).
%	\item Important weaknesses and flaws in the past design and evaluation of similar techniques \cite{DBLP:journals/eaai/MalialisK15}. We offer a deconstruction and empirical study on their formulation, flaws, and risk factors concerning different traffic distributions---in addition, we demonstrate modifications enabling deployment in real-world software-defined networks (\cref{sec:performance-in-an-emulated-environment}).
	\item Two source-level granularity approaches to RL-driven DDoS prevention (\emph{Instant} and \emph{Guarded} action models), improving upon past aggregate-based models (\cref{sec:ddos-mitigation-with-per-flow-reinforcement-learning}).
	\item An in-depth investigation into suitable features for an automatic DDoS mitigation system, with qualitative and quantitative justification (\cref{sec:rethinking-the-state-space}).
	\item Reactive simulations of HTTP and VoIP web-server traffic, designed to test system characteristics that packet trace playback fails to capture (\cref{sec:a-new-normal}).
	\item An empirical evaluation of our new models against the state-of-the-art in RL-based DDoS mitigation using these new traffic models (\cref{sec:the-results-of-doing-so}), alongside a discussion of security concerns and real-world deployment (\cref{sec:discussion}).
\end{itemize}

>>>>

\section{Introduction}
Network anomaly detection and intrusion detection/prevention are continually evolving problems, compounded by the partial, non-\emph{independent and identically distributed} (IID) view of data at each point in the network.
Attacks and anomalous behaviours evolve, becoming more sophisticated or employing new vectors to harm a network or system's confidentiality, integrity, and availability without being detected \cite{DBLP:journals/comsur/BhuyanBK14}.
These attacks and anomalies have measurable consequences and symptoms which allow a skilled analyst to infer new signatures for detection by misuse-based classifiers, but unseen attacks may only be defended against after-the-fact.
This issue is inherent to \emph{misuse-} or \emph{signature-based} intrusion detectors, and it has been long-hoped that \emph{anomaly-based} detectors would surpass this by making effective use of statistical measures \cite{DBLP:journals/comsur/BhuyanBK14}.

@@

%?? Discuss the most important conclusions before the outline.
We find that the existing work for this task \cite{DBLP:journals/eaai/MalialisK15} fails to account for congestion-aware traffic (i.e., TCP) and deployment environments with high host density per egress point, achieving poor results due to an overly coarse view of the network.
The approach we identify to remedy this is to make throttling decisions on a per-source basis, and we present the engineering decisions this mandates: updating RL agents from multiple traces per timestep, timed random sequential action computation and a supporting \emph{software-defined network} (SDN) architecture.
In tandem with the development and evaluation of an effective state space and model, we provide the design of a second model inspired by past work on algorithmic DDoS prevention, as an example of the integration of domain-specific knowledge.
Our introduction of per-source decisions improves substantially upon the state-of-the-art when acting upon most internet traffic (i.e., congestion-aware protocols), and we show that our second model achieves excellent performance for high host density in this case.
Crucially, both models remain protocol- and content-agnostic to offer future-proofing against the rollout of future protocols like QUIC \cite{DBLP:conf/sigcomm/LangleyRWVKZYKS17}.
%?? Also algorithmic enhancements such as multiple actions per timestep, 
%?? PROTOCOL-AGNOSTIC -- HOW WILL THESE THINGS COPE WITH QUIC ET AL.?!?!
Briefly, this paper contributes:
\begin{itemize}
%	\item A DDoS mitigation system based on direct-control reinforcement learning, designed for deployment in real-world software-defined networks (\cref{sec:environment-and-rl-algorithm,sec:acting-on-individual-sources}).
%	\item Important weaknesses and flaws in the past design and evaluation of similar techniques \cite{DBLP:journals/eaai/MalialisK15}. We offer a deconstruction and empirical study on their formulation, flaws, and risk factors concerning different traffic distributions---in addition, we demonstrate modifications enabling deployment in real-world software-defined networks (\cref{sec:performance-in-an-emulated-environment}).
	\item Two source-level granularity approaches to RL-driven DDoS prevention (\emph{Instant} and \emph{Guarded} action models), improving upon past aggregate-based models (\cref{sec:ddos-mitigation-with-per-flow-reinforcement-learning}).
	\item An in-depth investigation into suitable features for an automatic DDoS mitigation system, with qualitative and quantitative justification (\cref{sec:rethinking-the-state-space}).
	\item Reactive simulations of HTTP and VoIP web-server traffic, designed to test system characteristics that packet trace playback fails to capture (\cref{sec:a-new-normal}).
	\item An empirical evaluation of our new models against the state-of-the-art in RL-based DDoS mitigation using these new traffic models (\cref{sec:the-results-of-doing-so}), alongside a discussion of security concerns and real-world deployment (\cref{sec:discussion}).
\end{itemize}
